Path Model Temperature Comparisons

### 2016-07-15 path-temp-compare.Rmd
Add calculation of absolute umca density variables.

```{r load data, echo=F}
load("climate-path-model-data.RData")
library(piecewiseSEM); library(dplyr); library(lme4); library(lmerTest)
oakplots.sub$umca_density_m2 <- oakplots.sub$tot_bay / (15*15)
oakplots.sub$umca_density_m2.sqrt <- sqrt(oakplots.sub$umca_density_m2)
```

@@

```{r rescale variables}
## rescale variables
# oakplots.sub2$inf_bay.scl <- scale((oakplots.sub2$infected_bay_ct))
oakplots.sub$tot_bay.scl <- scale(oakplots.sub$tot_bay)
oakplots.sub$tot_bay.log.scl <- scale(oakplots.sub$tot_bay.log)
oakplots.sub$umca_basal_area.scl <- scale(oakplots.sub$umca_basal_area)
oakplots.sub$umca_ba.log.scl <- scale(oakplots.sub$umca_ba.log)
oakplots.sub$tot_lfct.scl <- scale(oakplots.sub$tot_lfct)
oakplots.sub$tot_lfct.log.scl <- scale(oakplots.sub$tot_lfct.log)
# oakplots.sub$avg_lfct.scl <- scale(oakplots.sub$avg_lfct)
oakplots.sub$hrs_abv25ds.scl <- scale(oakplots.sub$hrs_abv25ds)
oakplots.sub$avg_tmax_ds.scl <- scale(oakplots.sub$avg_tmax_ds)
oakplots.sub$avg_hrsblw14_wet_tminus1.scl <- scale(oakplots.sub$avg_hrsblw14_wet_tminus1)
oakplots.sub$hrs1422_wet_tminus1.log.scl <- scale(oakplots.sub$hrs1422_wet_tminus1.log)
# oakplots.sub$avg_hrs1422_wet_t_t1.scl <- scale(oakplots.sub$avg_hrs1422_wet_t_t1)
oakplots.sub$avg_hrs1422_wet_t_t1.log.scl <- scale(oakplots.sub$avg_hrs1422_wet_t_t1.log)

>>>>

```{r load data, echo=F}
load("climate-path-model-data.RData")
library(piecewiseSEM); library(dplyr); library(lme4); library(lmerTest)
oakplots.sub$umca_density_m2 <- oakplots.sub$tot_bay / (15*15)
oakplots.sub$umca_density_ha <- (oakplots.sub$tot_bay / (15*15))*10000
oakplots.sub$umca_density_m2.sqrt <- sqrt(oakplots.sub$umca_density_m2)
oakplots.sub$umca_density_ha.sqrt <- sqrt(oakplots.sub$umca_density_ha)
```

@@

```{r rescale variables}
## rescale variables
# oakplots.sub2$inf_bay.scl <- scale((oakplots.sub2$infected_bay_ct))
oakplots.sub$tot_bay.scl <- scale(oakplots.sub$tot_bay)
oakplots.sub$tot_bay.log.scl <- scale(oakplots.sub$tot_bay.log)
oakplots.sub$umca_density_m2.scl <- scale(oakplots.sub$umca_density_m2)
oakplots.sub$umca_density_m2.sqrt.scl <- scale(oakplots.sub$umca_density_m2.sqrt)
oakplots.sub$umca_basal_area.scl <- scale(oakplots.sub$umca_basal_area)
oakplots.sub$umca_ba.log.scl <- scale(oakplots.sub$umca_ba.log)
oakplots.sub$tot_lfct.scl <- scale(oakplots.sub$tot_lfct)
oakplots.sub$tot_lfct.log.scl <- scale(oakplots.sub$tot_lfct.log)
# oakplots.sub$avg_lfct.scl <- scale(oakplots.sub$avg_lfct)
oakplots.sub$hrs_abv25ds.scl <- scale(oakplots.sub$hrs_abv25ds)
oakplots.sub$avg_tmax_ds.scl <- scale(oakplots.sub$avg_tmax_ds)
oakplots.sub$avg_hrsblw14_wet_tminus1.scl <- scale(oakplots.sub$avg_hrsblw14_wet_tminus1)
oakplots.sub$hrs1422_wet_tminus1.log.scl <- scale(oakplots.sub$hrs1422_wet_tminus1.log)
# oakplots.sub$avg_hrs1422_wet_t_t1.scl <- scale(oakplots.sub$avg_hrs1422_wet_t_t1)
oakplots.sub$avg_hrs1422_wet_t_t1.log.scl <- scale(oakplots.sub$avg_hrs1422_wet_t_t1.log)
